Verifying the \shaThree\ Implementation from \openssl\ with the Software Analysis Workbench

### 2022-05-12 paper/fips202.tex
Add revisions for oppenssl text
Fix figures
Abstract while body, scale, and caption for figure 5.

\newsavebox{\RcCry}
\begin{lrbox}{\RcCry}
  \begin{lstlisting}[language=Cryptol, numbers=left, escapeinside={;}{;}]
    rc : [64] -> Bit
    rc t =  if (t % 255) == 0 then 1
            else rs !0 @0 where;\label{line:return};
              rs = [0b10000000] #;\label{line:init};
                   [if i <= t % 255 then;\label{line:compute};
                      (take'{8} ([(r@0) ^ (r@8),
                                   r@1, r@2, r@3, 
                                  (r@4) ^ (r@8),
                                  (r@5) ^ (r@8),
                                  (r@6) ^ (r@8),
                                   r@7,r@8])
                        where r = [0] # (rs @(i - 1)))
                    else rs @(i - 1);\label{line:stutter};
                   | i <- [1..254]];\label{line:alliters};
  \end{lstlisting}
\end{lrbox}

@@

\newsavebox{\RcCryLib}
\begin{lrbox}{\RcCryLib}
  \begin{lstlisting}[language=Cryptol, numbers=left, escapeinside={;}{;}]
    rc : [64] -> Bit
    rc t =  if (t % 255) == 0 then 1 
            else (while {i = 1, R = 0b10000000};\label{line:state};
                        (&state -> state.i <= t % 255);\label{line:cond};
                        (&state -> {
                          i = state.i + 1,;\label{line:inc};
                          R = (take'{8} ([(r@0) ^ (r@8),
                                           r@1, r@2, r@3,
                                          (r@4) ^ (r@8),
                                          (r@5) ^ (r@8),
                                          (r@6) ^ (r@8),
                                           r@7, r@8]) 
                                where r = [0] # state.R)})
                 ).R @0;\label{line:libreturn};
  \end{lstlisting}
\end{lrbox}

@@

Another common idiom in the \fips\ standard is to iteratively transform some state a fixed number of times to arrive at a final state.
The definition of the \emph{rc} function in \figref{fig:rc} is one such example.
The \emph{rc} function is a support function for the $\iota$ function in \keccak\ and is used to build a mask.

@@

@@

\begin{figure}[h]
  \begin{center}
    \begin{tabular}{l}
      \usebox{\RcCry} \\ \\
      \multicolumn{1}{c}{(a)} \\ \\
      \usebox{\whilemethod} \\ \\
      \multicolumn{1}{c}{(b)} \\ \\ 
      \usebox{\RcCryLib} \\ \\
      \multicolumn{1}{c}{(c)}
    \end{tabular}
  \end{center}
  \caption{The \emph{rc} function in \cryptol. (b) The \cryptol\ with list comprehensions. (b) The recursive while-method definition. (c) The \cryptol\ with the while-method.}
  \label{fig:rccry}
\end{figure}

>>>>

\newsavebox{\RcCry}
\begin{lrbox}{\RcCry}
  \begin{lstlisting}[language=Cryptol, numbers=left, escapeinside={;}{;}]
    rc : [64] -> Bit
    rc t =  if (t % 255) == 0 then 1
            else rs !0 @0 where;\label{line:return};
              rs = [0b10000000] #;\label{line:init};
                   [if i <= t % 255 then;\label{line:compute};
                      ((nextR r) where r = [0] # (rs @(i - 1)))
                    else rs @(i - 1);\label{line:stutter};
                   | i <- [1..254]];\label{line:alliters};
  \end{lstlisting}
\end{lrbox}

@@

\newsavebox{\RcCryLib}
\begin{lrbox}{\RcCryLib}
  \begin{lstlisting}[language=Cryptol, numbers=left, escapeinside={;}{;}]
    rc : [64] -> Bit
    rc t =  if (t % 255) == 0 then 1 
            else (while {i = 1, R = 0b10000000};\label{line:state};
                        (&state -> state.i <= t % 255);\label{line:cond};
                        (&state -> {
                          i = state.i + 1,;\label{line:inc};
                          R = (nextR r) where r = [0] # state.R})
                 ).R @0;\label{line:libreturn};
  \end{lstlisting}
\end{lrbox}

@@

Another common idiom in the \fips\ standard is to iteratively transform some state a fixed number of times to arrive at a final state.
The definition of the \emph{round constant}, \emph{rc}, function in \figref{fig:rc} is one such example.
The \emph{rc} function is a support function for the $\iota$ function in \keccak\ and is used to build a mask.

@@

\begin{figure}[t]
  \begin{center}
    \begin{tabular}{l}
      \usebox{\RcCry} \\ \\
      \multicolumn{1}{c}{(a)} \\ \\
      \usebox{\whilemethod} \\ \\
      \multicolumn{1}{c}{(b)} \\ \\ 
      \usebox{\RcCryLib} \\ \\
      \multicolumn{1}{c}{(c)}
    \end{tabular}
  \end{center}
  \caption{The \emph{rc} function in \cryptol. (a) The \cryptol\ with list comprehensions. (b) The recursive while-method definition. (c) The \cryptol\ with the while-method.}
  \label{fig:rccry}
\end{figure}

@@
